A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-15 paper.Rmd
create proper tables and reference them using dynamic references

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")
```

@@

Below is an example data dictionary table taken from the Tidy Tuesday repository on incarceration trends [@tidy-tuesday-incarcerate]. This includes information on the variable the class (type) of the variable, and a longer description of the variable.

__Table 1. The prisoner summary data dictionary, with columns on the variable, it's class, and a short description of the contents of the variable.__

|variable        |class     | Description |
|:---------------|:---------| :---------- |
|year            |integer (date)   | Year |
|urbanicity      |character | County-type (urban, suburban, small/mid, rural) |
|pop_category    |character | Category for population - either race, gender, or Total |
|rate_per_100000 |double    | Rate within a category for prison population per 100,000 people |

@@

The data dictionary provides _human readable_ information on the data. To ensure data types are preserved - dates are dates, names are characters, and so on - there needs to be some form of _machine readable_ metadata. An excellent standard for metadata is Table Schema written by frictionless data [@fritionless-table-schema]. Say for a dataset called "demographics" with three variables:

| age| height|nationality |
|---:|------:|:-----------|
|  12|  161.5|Australian  |
|  21|  181.2|American    |
|  37|  178.3|New Zealand |

_Table XX Example demographics table of age, height, and nationality._

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.width = "100%")

library(kableExtra)
```

@@

Table \@ref(tab:table-data-incarcerate) shows an example data dictionary table taken from the Tidy Tuesday repository on incarceration trends [@tidy-tuesday-incarcerate]. This includes information on the variable the class (type) of the variable, and a longer description of the variable.

```{r table-data-incarcerate}
dictionary_incarcerate <- data.frame(
  Variable = c("year", "urbanicity", "pop_category", "rate_per_100000"),
  Class  = c("integer (date)",
             "character",
             "character",
             "double"),
  description = c("Year",
                  "County-type (urban, suburban, small/mid, rural)",
                  "Category for population - either race, gender, or Total",
                  "Rate within a category for prison population per 100,000 people")
)

knitr::kable(dictionary_incarcerate,
             caption = "The prisoner summary data dictionary, with columns on the variable, it's class, and a short description of the contents of the variable.",
             booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position"))
```

@@

The data dictionary provides _human readable_ information on the data. To ensure data types are preserved - dates are dates, names are characters, and so on - there needs to be some form of _machine readable_ metadata. An excellent standard for metadata is Table Schema written by frictionless data [@fritionless-table-schema]. Say for a dataset called "demographics" with three variables (Table \@ref(tab:table-machine-readable))

```{r table-machine-readable}
table_machine_readable <- data.frame(
  age = c(12L, 21L, 37L),
  height = c(161.5, 181.2, 178.3),
  nationality = c("Australian", "American", "New Zealand")
)

knitr::kable(table_machine_readable,
             caption = "Example demographics table of age, height, and nationality.",
             booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position"))
```
